---
title: "mcprogress"
author: "Myles Lewis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mcprogress}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```

# Installation

Install from CRAN
```{r eval = FALSE}
install.packages("mcprogress")
```

Install from Github
```{r eval = FALSE}
devtools::install_github("myles-lewis/mcprogress")
```

# Example

This package adds a progress bar to `mclapply()` using `echo` to output to the
console in Rstudio or Linux environments. Simply replace your original call to
`mclapply()` with `pmclapply()`.

```{r eval=FALSE}
library(mcprogress)

# toy example
res <- pmclapply(letters[1:20], function(i) {
                 Sys.sleep(0.2 + runif(1) * 0.1)
                 setNames(rnorm(5), paste0(i, 1:5))
                 }, mc.cores = 2, title = "Working")

```

```{r eval=FALSE}
Working  |================================                 |  60%  eta 3.1 secs
```

The package also includes functions to safely print messages (including error
messages) from within parallelised code. This can be very useful for debugging
parallel R code.
